PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-21 paper.tex
Restructuring, WIP on content

As introduced, our aim is to build a dataset that can be used to train
machine-learning algorithms to both recognise and generate complex cognitive and
social dynamics in human-robot interactions. The Plymouth Interacting Social
Robots (PInSoRo) Dataset is such a novel dataset, comprising of \emph{natural
social} interactions arising between children, and recorded in a way suitable
for research methodologies based on machine learning. As detailed in
section~\ref{availablity}, this dataset is open and made freely available to any
interested researcher.

\subsection{The freeplay sandbox}

Critically, the acquisition of such a dataset requires first the definition of a
task to be performed by the participants while they are recorded. The nature of
this task influences in fundamental way the kind of interactions that might be
observed, and thus, learned.  Because they usually target very specific social
or cognitive skills in a tightly controlled manner, traditional socio-cognitive tasks are
either toy scenarios (\ie they do not adequately mirror real-world situations)
or simple, constrained tasks that do not reflect the complexity and dynamics of
real-world interactions. For this dataset, we aim on the contrary at a rich set
of naturally-occuring social interactions, and as such we have designed a novel
task that is:

\begin{itemize}
    \item be \textit{fundamentally social}, \ie the task would make little sense for an
        agent alone;
    \item foster rich \textit{multi-modal interaction}: simultaneous speech, gesture, and gaze
        behaviours are to be observed;
    \item exhibit \textit{non-trivial dynamics}, such as implicit turn-taking;
    \item should cover a \textit{broad range of interaction situations}.
\end{itemize}

@@

\subsection{Socio-cognitive Framing}

@@

\subsection{Implementation}

@@

@@

\subsection{Conditions}\label{conditions}

@@

\subsection{Demographics}\label{demographics}

@@

\subsection{Experimental Setup}\label{experimental-setup}

@@

\subsection{Acquisition Procedure}

@@

Total duration: 30 minutes per group.
\subsection{Initial Dataset Analysis}

@@

\subsection{Dataset availablity}
\label{availablity}

>>>>

The Plymouth Interacting Social Robots (PInSoRo) Dataset comprises of natural
social interactions arising between children, and recorded in a way suitable
for research methodologies based on machine learning.

As detailed in section~\ref{availability}, this dataset is open and made freely
available to any interested researcher. It is intended to be used to train
machine-learning algorithms (typically, deep recurrent network) to both
recognise and generate complex cognitive and social dynamics occurring in the
wild during social interactions.

\subsection{The Freeplay Sandbox}

The acquisition of such a dataset requires first the definition of a
task to be performed by the participants while they are recorded. The nature of
this task influences in fundamental way the kind of interactions that might be
observed, and thus, learned.  Because they usually target very specific social
or cognitive skills in a tightly controlled manner, traditional socio-cognitive tasks are
either toy scenarios (\ie they do not adequately mirror real-world situations)
or simple, constrained tasks that do not reflect the complexity and dynamics of
real-world interactions. For this dataset, we aim on the contrary at a rich set
of naturally-occurring social interactions, and as such we have designed a novel
task that:

\begin{itemize}
    \item is fundamentally social, \ie the task would make little sense for an
        agent alone;
    \item elicit a large range of interaction situations;
    \item foster rich multi-modal interaction: simultaneous speech, gesture, and gaze
        behaviours are to be observed;
    \item foster non-trivial social dynamics, such as implicit turn-taking.
\end{itemize}

@@

\subsubsection{Socio-cognitive Framing}

@@

\subsubsection{Implementation}

@@

\subsection{Dataset Acquisition}

@@

\subsubsection{Conditions}\label{conditions}

@@

\subsubsection{Demographics}\label{demographics}

@@

\subsubsection{Experimental Setup}\label{experimental-setup}

@@

\subsubsection{Acquisition Procedure}

@@

Total duration: 30 minutes per group.

\subsubsection{Initial Dataset Analysis}

@@

\subsection{Dataset availability}
\label{availability}
